Long--term perspectives of social inequality in mortality among adults and elderly in northern Sweden 1851--2013\footnote{Session "Health and Mortality in Arctic Populations" at The Ninth International Congress on Arctic Social Sciences (ICASS IX) June 11, 2017, Umeå}

### 2017-06-09 Umea.Rnw
Last corrections

\title{Long--term perspectives of social inequality in mortality among adults and elderly in
  northern  Sweden 1851--2013\footnote{Session "Health and Mortality in Arctic Populations" at The Ninth International Congress on Arctic Social Sciences (ICASS IX) June 10, 2017, Umeå}
}

\date{\today}

@@

To investigate the association between social class and mortality among adults and elderly from the 19th century to the present and how it is connected to socio-economic inequality in society.
This is analysed according to 
\begin{itemize}
\item gender
\item age group (working age vs retired)
\item cause of death (cardiovascular, cancer)
\item (education 1990--2013)
\item (income 1986-2005)

@@

\item[sex]
\item[birth date] By quarter (15 Feb, May, Aug, Nov)
\item[death date] By day (\emp{Socialstyrelsen})
\item[cause of death] from \emp{Socialstyrelsen}
\item[parish] Urban/Rural
\item[Social class] Elite, middle, worker. Household definition 1851--1950. Individual definition 1960--2013
\item[income] 1990--2005, grouped by quartiles.
\item[education] 1990--2005, three categories.
\item[period]  1851--1875, \ldots,  2008--2013 (10 periods). No results presented for women 1961-70, 1971-80 due to missing information on class.
%\item[cohort] 1761--1771, \ldots, 1971--1974 (22 birth cohorts).

@@

\begin{itemize}
  \item \emp{\tt sex}
  \item \emp{\tt period}: 1851--75, 1876--1900, 1901--10, etc.
  \item \emp{\tt class}
  \item \emp{\tt age group}: 40--64, 65--89.
  \item \emp{\tt cause of death}
\end{itemize}
\end{frame}

>>>>

\title{Long--term perspectives of social inequality in mortality among adults and elderly in
  northern  Sweden 1851--2013\footnote{Session "Health and Mortality in Arctic Populations" at The Ninth International Congress on Arctic Social Sciences (ICASS IX) June 11, 2017, Umeå}
}

\date{June 11, 2017}

@@

To investigate the association between social class and mortality among adults and elderly from the 19th century to the present and how it is connected to socio-economic inequality in society.
This is analysed according to 
\begin{itemize}
\item gender
\item age group (working age vs retired)
\item *cause of death (cardiovascular, cancer)
\item *education 1990--2013
\item *income 1986-2005

@@

\item[Sex]
\item[Marital status]
\item[Birth date] By quarter (15 Feb, May, Aug, Nov)
\item[Death date] By day (\emp{Socialstyrelsen})
\item[Cause of death] from \emp{Socialstyrelsen}
\item[Parish] Urban/Rural
\item[Social class] Elite, middle, worker. Household definition 1851--1950. Individual definition 1960--2013
\item[Income] 1990--2005, grouped by quartiles.
\item[Education] 1990--2005, three categories.
\item[Period]  1851--1875, \ldots,  2008--2013 (10 periods). No results presented for women 1961-70, 1971-80 due to missing information on class.
%\item[cohort] 1761--1771, \ldots, 1971--1974 (22 birth cohorts).

@@

\begin{itemize}
  \item \emp{\tt sex}
  \item \emp{\tt period}: 1851--75, 1876--1900, 1901--10, etc.
  \item \emp{\tt class}
  \item \emp{\tt age group}: 40--64, 65--89.
  \item \emp{\tt *cause of death}
\end{itemize}
\end{frame}
